\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=12pt, itemsep=2pt, topsep=2pt}
\pagestyle{empty}

\begin{document}

\begin{center}
{\LARGE Alex Chen} \\
San Francisco, CA \textbar{} alex.chen@example.com \textbar{} (555) 123-4567 \\
\href{https://linkedin.com/in/alexchen}{linkedin.com/in/alexchen}
\textbar{}
\href{https://github.com/alexchen}{github.com/alexchen}
\end{center}

\vspace{4pt}
\textbf{Summary} \\
Senior Software Engineer with 8+ years building distributed backend systems and
internal developer platforms. Led multi-team initiatives that improved API
latency, service reliability, and release velocity across high-traffic
production environments.

\vspace{6pt}
\textbf{Experience}

\vspace{4pt}
\textbf{Nimbus Commerce} \hfill San Francisco, CA \\
\textit{Senior Software Engineer} \hfill 2021 -- Present
\begin{itemize}
  \item Led migration of checkout services from monolith modules to domain
  APIs, reducing p95 latency by 37\% and supporting 4x seasonal traffic.
  \item Designed an idempotent order pipeline with retry-safe semantics and
  event audit trails, lowering duplicate charge incidents by 92\%.
  \item Built deployment health gates and rollback automation used by 14 teams,
  reducing failed production rollouts by 46\%.
\end{itemize}

\textit{Software Engineer II} \hfill 2018 -- 2021
\begin{itemize}
  \item Built inventory reservation service in Go and PostgreSQL handling
  120M+ daily requests with strict consistency checks.
  \item Added real-time SLA dashboards and alerting playbooks, cutting
  mean-time-to-detect by 55\% during peak events.
\end{itemize}

\vspace{4pt}
\textbf{Orbit Analytics} \hfill Seattle, WA \\
\textit{Software Engineer} \hfill 2016 -- 2018
\begin{itemize}
  \item Implemented streaming ingestion pipeline for customer telemetry,
  reducing data freshness from 25 minutes to under 4 minutes.
  \item Partnered with product and support to ship self-serve diagnostics
  tooling that reduced L2 ticket volume by 30\%.
\end{itemize}

\vspace{6pt}
\textbf{Selected Projects}
\begin{itemize}
  \item \textbf{Service Scorecard Platform}: Internal quality scorecards for 70+
  services using reliability, test coverage, and change failure metrics.
  \item \textbf{Incident Review Assistant}: Automated extraction of action items
  from postmortems with ownership assignment and due-date tracking.
\end{itemize}

\vspace{6pt}
\textbf{Education} \\
M.S. Computer Science, Georgia Institute of Technology \hfill 2020 \\
B.S. Computer Science, University of Washington \hfill 2016

\vspace{6pt}
\textbf{Skills} \\
Go, Python, TypeScript, Java, PostgreSQL, Redis, Kafka, gRPC, Kubernetes,
Terraform, AWS, CI/CD, Observability, Incident Response

\end{document}
